% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Work Experience at the top
\sectionTitle{Professional experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}

\begin{experiences}
    \experience
        {May 2019}
        {.Net \& Cloud Developer}
        {WeMakeIoT}
        {Present}
        {
            \begin{itemize}
                \item Define cloud architecture, design, and implement applications on Azure.
                \item Architect solutions using MS Azure services such as IoT Hub, Web App service, Azure Functions, Cosmos DB, and identity management solutions like Azure AD.
                \item Power BI integration with Azure to create dashboards.
                \item Developing ASP.NET Core website and Web API solutions to be hosted on Azure.
                \item Create a webserver on ESP32 to monitor and control devices.
				\item Designing and developing software applications with Microsoft .NET Framework using MVC and SQL Server.
				\item Deploying to IIS servers.
            \end{itemize}
        }
        {
            C\#,
            .NET Core,
            ASP.NET 4.65/4.5,
            Entity Framework,
            LINQ,
            SQL,
            AJAX,
            HTML, 
            CSS, 
            JavaScript,
            jQuery,
            IIS,
            Azure IoT, 
            Azure Cosmos DB, 
            Azure Functions,
            Azure Active Directory
        }

    \emptySeparator

    \experience
        {April 2017}
        {Senior Developer and Team Lead}
        {OHO Software Innovations}
        {April 2019}
        {
            \begin{itemize}
                \item Led end-to-end report development process from definition of business requirements to distribution of finalized product.
                \item Maintain and monitor project timelines and ensure accuracy in reporting of project status.
                \item Worked in all stages of SDLC (Software Development Life Cycle) involving studying of the user requirements, analyzing, designing, coding, implementation, debugging, testing, deployment and documentation.
                \item Hands on technology experience of designing and developing software applications with Microsoft .NET Framework 4.0 using C# and ADO.Net.
                \item Proficiency in Visual Studio 2013 and hands on experience with SQL Server 2014.
                \item Experience with Data Accessing including using Data Adapter, Data Reader and Dataset in ADO.NET and LINQ (Language Integrated Query) Providers for data manipulation.
                \item Worked extensively on writing Stored Procedures, Functions, Views and Database Design.
                \item Experience in software unit testing and efficient at fact-finding, root cause analysis and bug-fixing.
                \item Migration of classic Foxpro applications to C#, DBF to SQL Server.
            \end{itemize}
        }
        {
            C\#,
            WinForms,
            ASP.NET 4.5/4.0/3.5,
            ADO.Net,
            RDLC,
            SSRS,
            LINQ,
            SQL,
            AJAX,
            HTML, 
            CSS, 
            JavaScript,
            jQuery,
            IIS
        }

    \emptySeparator

    \experience
        {January 2016}
        {.Net and SQL Server Developer}
        {OHO Software Innovations}
        {April 2017}
        {
            \begin{itemize}
                \item Worked with ADO.NET objects to connect to the databases.
                \item Developed advanced SQL queries with multi-table joins, group functions, subqueries, set operations and T-SQL stored procedures, user defined functions (UDFs) for data analysis.
                \item Designed and developed stored procedures, queries and views necessary to support SSRS reports for an existing ERP software
                \item Developed accessible intranet applications in Visual Studio 2013 using JavaScript, C# with ASP.Net, and SQL Server
                \item Deploying to IIS servers and performing website set up in IIS
                \item Maintained and Modified existing Intranet web applications
            \end{itemize}
        }
        {
            C\#,
            WinForms,
            ASP.NET 4.5/4.0/3.5,
            ADO.Net,
            RDLC,
            SSRS,
            LINQ,
            SQL,
            AJAX,
            HTML, 
            CSS, 
            JavaScript,
            jQuery,
            IIS
        }

    \emptySeparator

    \experience
        {August 2014}
        {Intern}
        {GadgEon Smart Systems Pvt Ltd.}
        {July 2015}
        {
            \begin{itemize}
                \item Internship as part of M.Tech course.
                \item Developed a real-time data system on Linux using Programmable Real-time Units on AM335x SoC
            \end{itemize}
        }
        {
            Embedded C
        }

    \emptySeparator

    \experience
        {September 2006}
        {Software Engineer}
        {Infosys}
        {February 2008}
        {
            \begin{itemize}
                \item Coded mainframe development in COBOL, modified tables in DB2, created job cards in JCL to run batch jobs, and modified online screens using CICS.
                \item Created Unit Test Documents containing test case procedure, data sources, results, and screen captures highlighting input and output data, indicators, and system display statements
            \end{itemize}
        }
        {
            COBOL, 
            DB2,
            JCL, 
            CICS, 
            Java, 
            JSP
        }

\end{experiences}
